Template Master's Thesis

### 2023-08-20 paper.tex
Update discussion - Add network visualization of aggregating address
Update discussion

Our implementation of node embedding methods differs from previous approaches by \cite{Beres2020} and \cite{wu2022tutela}, the main reason being different settings and research questions. We construct the network graph based on the asset transfers within our address set and simultaneously analyze Polygon and Ethereum data. \newline

@@

Moreover, we validated our approach and found better results in terms of average rank of ENS pairs, when building the network graph out of intra-set asset transfers compared to using all token transfer events and/or transactions. A possible extension would include incorporating edge weights, similar to \cite{wu2022tutela}, however, we refrained from doing this because we would have needed to implement a custom node embedding algorithm.\newline

@@

While our clustering method may not be ideal, it is probably more effective than, for example, clustering a fixed number of $k$ neighbors. We observed that the number of clusters and their size is highly sensitive to the chosen distance threshold, making it challenging to assess the accuracy of these clusters. We have provided a sensitivity analysis to illustrate this issue. The distances between the feature vectors tend to be quite narrow, with significant variation even among various ground truth pairs' distances. Regardless of the distance threshold, we were able to locate a cluster of 500+ addresses. Manual inspection revealed that these address show very similar on-chain patterns: They are only active on Polygon, most of the transfers are NFT mints and all NFTs are somehow related to Decentraland. Further, they transfer specific NFTs to the same address. Unsere Vermutung ist dass es ein Bot ist der mit vielen verschiedenen Adressen auf Decentraland aktiv ist, an verschiedene Orte/Events geht um dort NFT airdrops zu erhalten. Wenn sie etwas wert sind aggregiert er die NFTs auf eine addresse und verkauft sie über den marketplace. Man könnte diese Vermutung mit den bewegungsdaten validieren/überprüfen. Spannend dass der node embedding algo trotz limiterten informationen dieses pattern entdeckt hat. Etwas das in zukunft ein problem werden könnte -> evtl. sehr viel Bot aktivität auf DCL und evtl. mehr Research reinfliessen könnte.

We explored potential enhancements to our method, such as incorporating additional information, e.g., time-of-day-activity and/or gas price selection into the feature vectors. Unfortunately, these modifications did not yield improvements. %vielleicht auch falsch gemacht
Similarly, a two-step approach to clustering also proved unsuccessful. These areas remain open for future research.

%Moreover, when evaluating different network graphs as the starting point to create node embeddings we found better results in terms of average rank with the intra-set asset transfer dataset, instead of using all transfer events and/or transactions.

%\textbf{LAND transfers}\\
The \textit{LAND transfer} heuristic again looks at very specific on-chain behavior.  740 transfers, 413 addressen und 161 or 160 entities with 342 addresses. -The large cluster may incorrectly be marked/maybe off-chain compensation? -> auction address

 We use the fact that these addresses are related to Decentraland and therefore choose LAND. But this could also be applied to other NFTs or large ERC20 token/Ether/stablecoin transfers. Main reasoning: revealing clusters by sending high-value amount to other address why? reorganize wallet(s), upgrade security, increased value of NFTs/assets over time -> change from metamask (starting option) to hardware wallet.

 Pro: lässt sich gut visualisieren und evtl. auch nachvollziehen
 Kontra: Likely a lot of false-positives with this appraoch, could be something missing in the on-chain data.

%eigener approach hat ein spezifisches on-chain event zur voraussetzung, basiert auf annahme dass LAND nicht einfach so weitergegeben wird, ist auch auf andere nfts oder grosse token transfers anwendbar. hat auch funktioniert aber wieder relativ wenige clusters gefunden, hat es falsch positive dabei? zb. offchain zahlungen und on-chain token transferiert
%%%%%%%%%%%%%%%%%%%%%

Diskutiere alle resultate gemeinsam, vom anfangs set über on-chain und intra-set zu den clusters.
470k -> 135k on chain -> 51k intra-set transfer -> etc.

other Limitations -> ENS pairs? Incorporate time-of-day/normalized gas into feature vectors, two step approach

@@

%% Table
\begin{table}[h!]
  \centering
  \tiny
  \begin{tabular}{ll p{4cm} l}
    \hline
    \textbf{Collection} & \textbf{Fields} & \textbf{Description} & \textbf{Example} \\ \hline
    Transactions & \texttt{\_id} & Unique identifier & 64b3c65ed2daf924bfdce72b
 \\
    (16,184,993 rows) & \texttt{hash} & Transaction hash & 0x8d9490e9f0992e68490cfcb126e76290eca3bf668a... \\
     & \texttt{timeStamp} & Timestamp in seconds from the UNIX epoch &  1657777314\\
     & \texttt{gasUsed} & Amount of gas used by the transaction &  144176  \\
     & \texttt{gasPrice} & The price of gas the originator is willing to pay &  12449848873 \\
     & \texttt{nonce} &   &   \\
     & \texttt{from} & Address initiating the transaction &   \\
     & \texttt{to} & The destination address (either native asset transfer or function call) &  \\
     & \texttt{value} & The amount of Ether/Matic to send to the destination & 500 \\
     & \texttt{input} & Calldata & 0x095ea7b30000000000000000000000001111111254fb6c44bac0bed2854e76f90643097dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff \\
     & \texttt{functionName} & added by Etherscan & approve(address spender, uint256 rawAmount) \\
     & \texttt{chainName} & Chain indicator & Ethereum or Polygon \\
    \hline
    Transfers & \texttt{\_id} & see above & see above\\
    (36.4M rows) & \texttt{hash} & see above & see above \\
     & \texttt{timeStamp} & see above & see above\\
     & \texttt{gasUsed} & see above &  see above\\
     & \texttt{gasPrice} & see above & see above \\
     & \texttt{nonce} &  see above & see above \\
     & \texttt{from} &  Sender address & see above \\
     & \texttt{to} &  Recipient address & see above \\
     & \texttt{value} & Amount of tokens transferred in Wei, only for fungible or semi-fungible tokens & 10000000000000000 or NaN (ERC-721) \\
     & \texttt{tokenID} &  Identifier of the NFT or semi-fungible token &  or NaN (ERC20) \\
     & \texttt{contractAddress} & The token contract address &  0xc02aaa39b223fe8d0a0e5c4f27ead9083c756cc2 \\
     & \texttt{tokenName} & The specified token name &  Wrapped Ether\\
     & \texttt{tokenType} & Token standard indicator &  20 or 721 or 1155\\
     & \texttt{chainName} & see above &  see above \\
     & \texttt{isSet} & Indicator if from or to address are from address set &  from or to \\
     & \texttt{userAddress} & Address of interested user & 0x000000085d9a759bb5c3d459d638739c0f48deb0\\
    \hline
  \end{tabular}
  \caption{Database/Dataset Description}
  \label{tbl:database_schema}
\end{table}

>>>>

Our implementation of node embedding methods differs from previous approaches by \cite{Beres2020} and \cite{wu2022tutela}, the main reason being different settings and research questions. We construct the network graph based on asset transfers within our address set and simultaneously analyze Polygon and Ethereum data. \newline

@@

Moreover, we validated our approach and found better results in terms of average rank of ground truth address pairs, when building the network graph out of intra-set asset transfers compared to using all token transfer events and/or transactions. A possible extension would include incorporating edge weights, similar to \cite{wu2022tutela}, however, we refrained from doing this because we would have needed to implement a custom node embedding algorithm.\newline

@@

While our clustering method may not be ideal, it is probably more effective than clustering a fixed number of $k$ neighbors for each node. We observed that the number of clusters and their size is highly sensitive to the chosen distance threshold, making it challenging to assess the accuracy of these clusters. We have provided a sensitivity analysis to illustrate this issue. The distances between the feature vectors tend to be quite narrow, with significant variation even among various ground truth pairs' distances. Regardless of the threshold value, we were able to locate a cluster of more than 500 addresses. Manual inspection revealed that these address show very similar on-chain patterns: They are all exclusively active on Polygon and most of the transfers are mints of Decentraland related NFTs. Further, they transfer some NFTs to address \texttt{0xE2e2F2240a84A61B7dFF50a86ee10d5FaF7faCa8}. The transfers to and from this address are shown in Figure \ref{fig:cluster}. Incoming transfers are indicated by green edges, while outgoing transfers are shown by red edges. We hypothesize that the network in question may be operated by a user/bot that creates multiple distinct addresses and actively engages with Decentraland. It seems likely that this bot may target specific locations or events where NFTs are (automatically) air-dropped to avatars in presence. If these NFTs hold value, the bot may then aggregate them to the main address and sell them on the Decentraland marketplace. This hypothesis could be verified with the Decentraland movement data. Notably, despite the limited on-chain data available, the node embedding algorithm was able to detect this activity pattern.
Bot activity may become a problem for open and permissionless metaverse platforms like Decentraland and an interesting topic for future research. \newline
Finally, we explored potential enhancements to the graph representation learning method, such as incorporating time-of-day-activity and/or gas price selection data into the feature vectors. Unfortunately, these modifications did not yield improvements. %vielleicht auch falsch gemacht
Similarly, a two-step approach to clustering also proved unsuccessful. These areas remain open for future research.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\textwidth]{../figures/network_visualization_0xe2e.png}
	\caption{Token Transfer Graph for \texttt{0xE2e2F$\dots$faCa8}}
	\label{fig:cluster}
\end{figure}

%\textbf{LAND transfers}\\
The \textit{LAND transfer} heuristic is targeted at users revealing address clusters by sending high-value assets to other addresses. In this specific case, we use the information that all addresses are related to Decentraland and therefore analyze LAND transfers. However, the approach could be applied (more generally) to other NFT collections or large asset transfers in general. \newline
The main intuition/assumption behind this approach is that users may want to reorganize their accounts from time to time, mostly to increase security guarantees or spread the risk around multiple accounts. As a concrete example, some users may have started with a simple browser-based wallet but as the value of their assets and their knowledge grew, they changed to a more secure hardware wallet. We detect 161 entities with 413 addresses applying this approach. One entity with 70 address is very likely a false-positive, including an address that participated in the intial LAND auction and subsequently distributed LAND. This may have happened through some off-chain compensation. The advantage of this method is that it is relatively easy to visualise and understand. The disadvantage is that it demands a specific on-chain behaviour and is only scalable with significant effort. Additionally, many events that occur off-chain are not detectable in the data, resulting in an increased occurrence of false positives.

%Moreover, when evaluating different network graphs as the starting point to create node embeddings we found better results in terms of average rank with the intra-set asset transfer dataset, instead of using all transfer events and/or transactions.
%740 transfers, 413 addressen und 161 or 160 entities with 342 addresses. -The large cluster may incorrectly be marked/maybe off-chain compensation? -> auction address
%%%%%%%%%%%%%%%%%%%%%

In this thesis, we set out to cluster 470k addresses observed in Decentraland. Focusing on on-chain data on Ethereum and Polygon, we reduced the address set to 135k. Depending on various assumptions, we were able to cluster entities interacting through more than one address. Merging the clusters resulting after applying each of the three clustering heuristics and assuming a treshold value of 0.5 for node embedding, we could cluster X addresses to Y entities. Assuming that all other addresses are single clusters, we argue that the total number of active users during that time frame was ...

other Limitations -> ENS pairs? Incorporate time-of-day/normalized gas into feature vectors, two step approach
Limitations: various assumptions, possibly false-positives, some clusters may well be undetected.

%Diskutiere alle resultate gemeinsam, vom anfangs set über on-chain und intra-set zu den clusters.
470k -> 135k on chain -> 51k intra-set transfer -> etc.

@@

%% Table
\begin{table}[h!]
  \centering
  \tiny
  \begin{tabular}{ll p{4cm} l}
    \hline
    \textbf{Collection} & \textbf{Fields} & \textbf{Description} & \textbf{Example} \\ \hline
    Transactions & \texttt{\_id} & Unique identifier & 64b3c65ed2daf924bfdce72b
 \\
    (16.1M rows) & \texttt{hash} & Transaction hash & 0x8d9490e9f0992e68490cfcb126e76290eca3bf668a... \\
     & \texttt{timeStamp} & Timestamp in seconds from the UNIX epoch &  1657777314\\
     & \texttt{gasUsed} & Amount of gas used by the transaction &  144176  \\
     & \texttt{gasPrice} & The price of gas the originator is willing to pay &  12449848873 \\
     & \texttt{nonce} &   &   \\
     & \texttt{from} & Address initiating the transaction &   \\
     & \texttt{to} & The destination address (either native asset transfer or function call) &  \\
     & \texttt{value} & The amount of Ether/Matic to send to the destination & 500 \\
     & \texttt{input} & Calldata & 0x095ea7b30000000000000000000000001111111254fb6c44bac0bed2854e76f90643097dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff \\
     & \texttt{functionName} & added by Etherscan & approve(address spender, uint256 rawAmount) \\
     & \texttt{chainName} & Chain indicator & Ethereum or Polygon \\
    \hline
    Transfers & \texttt{\_id} & see above & see above\\
    (36.4M rows) & \texttt{hash} & see above & see above \\
     & \texttt{timeStamp} & see above & see above\\
     & \texttt{gasUsed} & see above &  see above\\
     & \texttt{gasPrice} & see above & see above \\
     & \texttt{nonce} &  see above & see above \\
     & \texttt{from} &  Sender address & see above \\
     & \texttt{to} &  Recipient address & see above \\
     & \texttt{value} & Amount of tokens transferred in Wei, only for fungible or semi-fungible tokens & 10000000000000000 or NaN (ERC-721) \\
     & \texttt{tokenID} &  Identifier of the NFT or semi-fungible token &  or NaN (ERC20) \\
     & \texttt{contractAddress} & The token contract address &  0xc02aaa39b223fe8d0a0e5c4f27ead9083c756cc2 \\
     & \texttt{tokenName} & The specified token name &  Wrapped Ether\\
     & \texttt{tokenType} & Token standard indicator &  20 or 721 or 1155\\
     & \texttt{chainName} & see above &  see above \\
     & \texttt{isSet} & Indicator if from or to address are from address set &  from or to \\
     & \texttt{userAddress} & Address of interested user & 0x000000085d9a759bb5c3d459d638739c0f48deb0\\
    \hline
  \end{tabular}
  \caption{Database/Dataset Description}
  \label{tbl:database_schema}
\end{table}
